Historical trends in the contribution of six major causes of death to the black-white

### 2017-04-13 Manuscript/Manuscript_COD_Trends.Rmd
stacked line charts

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")
```

@@

>>>>

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")

cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))
```

@@

**Men**

```{r stacked_trends_male, echo=F, fig.height=9, fig.width=11}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Male"), aes(x = year, y = COD_cont_yrs_mean)) + 
  geom_hline(aes(yintercept = 0)) + geom_vline(aes(xintercept = 1969)) + geom_hline(aes(yintercept = -0.4)) + #the axes
  geom_area(aes(fill = COD_rev), stat = "identity") +
  facet_wrap( ~ stabbrs.map.order, ncol = 11, drop = F) + 
  theme_classic(base_size = 10) + 
  theme(axis.text.x = element_blank(),
        strip.background=element_blank(),
        axis.line=element_blank(),
        axis.ticks=element_blank()) +
  ylab("Contribution to the life expectancy gap (%)") +
  xlab("Year (1969-2013)"))

ggplotly(ggplot(subset(cod_decomp_results, sex == "Male" & year > 2009), aes(x = year, y = COD_cont_yrs_mean)) + 
  geom_hline(aes(yintercept = 0)) + geom_vline(aes(xintercept = 2009)) + geom_hline(aes(yintercept = -0.4)) + #the axes
  geom_area(aes(fill = COD_rev), stat = "identity") +
  facet_wrap( ~ stabbrs.map.order, ncol = 11, drop = F) + 
  theme_classic(base_size = 10) + 
  theme(axis.text.x = element_blank(),
        strip.background=element_blank(),
        axis.line=element_blank(),
        axis.ticks=element_blank()) +
  ylab("Contribution to the life expectancy gap (%)") +
  xlab("Year (2009-2013)"))
```

**Women**

```{r stacked_trends_female, echo=F, fig.height=9, fig.width=11}
ggplotly(ggplot(subset(cod_decomp_results, sex == "Female"), aes(x = year, y = COD_cont_yrs_mean)) + 
  geom_hline(aes(yintercept = 0)) + geom_vline(aes(xintercept = 1969)) + geom_hline(aes(yintercept = -0.4)) + #the axes
  geom_area(aes(fill = COD_rev), stat = "identity") +
  facet_wrap( ~ stabbrs.map.order, ncol = 11, drop = F) + 
  theme_classic(base_size = 10) + 
  theme(axis.text.x = element_blank(),
        strip.background=element_blank(),
        axis.line=element_blank(),
        axis.ticks=element_blank()) +
  ylab("Contribution to the life expectancy gap (%)") +
  xlab("Year (1969-2013)"))

ggplotly(ggplot(subset(cod_decomp_results, sex == "Female" & year > 2009), aes(x = year, y = COD_cont_yrs_mean)) + 
  geom_hline(aes(yintercept = 0)) + geom_vline(aes(xintercept = 2009)) + geom_hline(aes(yintercept = -0.4)) + #the axes
  geom_area(aes(fill = COD_rev), stat = "identity") +
  facet_wrap( ~ stabbrs.map.order, ncol = 11, drop = F) + 
  theme_classic(base_size = 10) + 
  theme(axis.text.x = element_blank(),
        strip.background=element_blank(),
        axis.line=element_blank(),
        axis.ticks=element_blank()) +
  ylab("Contribution to the life expectancy gap (%)") +
  xlab("Year (2009-2013)"))
```
